---
title: "B: Simulation code"
author: Marcel Miché
date: 2023-07-31
output:
  html_document:
    theme: yeti
    toc: false
vignette: >
  %\VignetteIndexEntry{B: Simulation code}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Table 1 in the manuscript contains the following information:

* The analyzed sample size was 4050.
* 205 participants reported a lifetime suicide attempt (assessed at study baseline).
* 2197 participants were diagnosed with any lifetime mental disorder (assessed at baseline).
* 1841 participants were male, 2209 were female.
* Age (obtained at baseline; mean and standard deviation) was 53.89 and 11.09, respectively. Age ranged between 35.84 and 85.57.
* The outcome suicide attempt at any of the three follow-up assessments were reported by 48 participants.

*BEWARE*: Only if the below code is executed without any changes, the simulated dataset will be superficially similar to the original dataset. Especially will the simulated outcome be 'the same', as in the original dataset: 4002 non-cases, 48 cases.

Info: The set.seed(1) command (see code below) guarantees perfect reproducibility across users and operating systems.

## Simulate original data
```{r echo=TRUE}
# psa: prior suicide attempt
psa <- rep(c(0,1), times=c(3845, 205))
# pmd: prior mental disorder
pmd <- rep(c(0,1), times=c(1853, 2197))
# sex (0 = male, 1 = female)
sex <- rep(c(0,1), times=c(1841, 2209))
# age: Sample 100'000 values from normal distribution with mean and sd same as in the real dataset.
set.seed(1)
age0 <- rnorm(n=100000, mean=53.89, sd = 11.09)
# Select 4050 values in the age range of the real dataset.
set.seed(1)
age <- sample(age0[age0>=35.84 & age0<=85.57], size=4050)
# The logistic regression coefficients that were obtained for the original dataset, were (intercept, psa, pmd, sex, age):
# c(-4.0296, 2.5446, 1.7113, -0.0631, -0.0423)
# linear combination
z = -4.0296 + 2.5446*psa + 1.7113*pmd - 0.0631*sex - 0.0423*age
# Use inverse logit function to produce pr (probabilities)
pr = 1/(1+exp(-z))
# Mess up these probabilities a little bit to introduce noise.
sampleFrom <- seq(0, .002975, by=.00001)
set.seed(1)
changeProbsBy <- sample(sampleFrom, size=4050, replace=TRUE)
pr <- pr + changeProbsBy
# Compute the simulated outcome fsa (future suicide attempt)
set.seed(1)
fsa <- rbinom(4050, 1, pr)
# Make the simulated dataset, which is closely based on the real dataset.
simData <- data.frame(fsa=factor(fsa), psa, pmd, sex, age)

# Summary (compare with table 1 in the manuscript), age is a little different.
summary(simData) # Simulated mean outcome = 0.01185 (1.185%)
```

## Results of original PsyCoLaus data

Original PsyCoLaus data (overview computed with the rms package).
```{r echo=TRUE}
#                        Model Likelihood    Discrimination    Rank Discrim.
#                              Ratio Test           Indexes          Indexes
# Obs          4050    LR chi2      94.95    R2       0.192    C       0.821
#  0           4002    d.f.             4    g        1.379    Dxy     0.642
#  1             48    Pr(> chi2) <0.0001    gr       3.971    gamma   0.645
# max |deriv| 3e-05                          gp       0.015    tau-a   0.015
#                                            Brier    0.011
# 
#           Coef    S.E.   Wald Z Pr(>|Z|)
# Intercept -4.0296 0.9735 -4.14  <0.0001
# SUA2       2.5446 0.3096  8.22  <0.0001
# mentalDx   1.7113 0.5346  3.20  0.0014
# Sex       -0.0631 0.3100 -0.20  0.8388
# Age       -0.0423 0.0165 -2.56  0.0105
```

Simulated data (overview computed with the rms package)
```{r echo=TRUE}
 #                       Model Likelihood    Discrimination    Rank Discrim.    
 #                             Ratio Test           Indexes          Indexes    
 # Obs         4050    LR chi2      76.56    R2       0.155    C       0.804    
 #  0          4002    d.f.             4    g        1.317    Dxy     0.608    
 #  1            48    Pr(> chi2) <0.0001    gr       3.731    gamma   0.612    
 # max |deriv| 0.03                          gp       0.015    tau-a   0.014    
 #                                           Brier    0.011                     
 # 
 #           Coef    S.E.    Wald Z Pr(>|Z|)
 # Intercept -3.8455  0.9662 -3.98  <0.0001 
 # psa        2.1145  0.3157  6.70  <0.0001 
 # pmd        5.5099 41.3914  0.13  0.8941  
 # sex       -3.7471 41.3940 -0.09  0.9279  
 # age       -0.0431  0.0161 -2.67  0.0077
```

## Explanation of coefficient names in both results' outputs:
* SUA2 and psa: Any lifetime suicide attempt.
* mentalDx and pmd: Any lifetime mental disorder diagnosis.
* Sex: Biological sex (male or female)
* Age: Age in years

All four predictors were assessed at study baseline.

**References**

Package citations, enter in R console: ?predictSuiattPsyCoLaus::predictSuiattPsyCoLaus

Then, on that help page, scroll down to References.