---
title: "C: Logistic regression"
author: Marcel Miché
date: 2023-06-02
output:
  html_document:
    theme: yeti
    toc: false
vignette: >
  %\VignetteIndexEntry{C: Logistic regression}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## All code to obtain predictions, using logistic regression

### Load required R packages (install first, if not yet installed)
```{r echo=TRUE, eval = FALSE}
# Load packages (install if not yet installed)
# tidyverse: Allround package, e.g., visualizations with ggplot2
library(tidyverse)
# precrec: precision-recall curve statistics
library(precrec)
```

### Set up the 80/20 training/test holdout resampling.
```{r echo=TRUE, eval = FALSE}
# Holdout proportion of full sample, use for training: 80%
holdoutTrain <- .8
# Remaining proportion of full sample, use for testing: 20%
(holdout <- c(holdoutTrain, 1-holdoutTrain))
```

### Own function to apply the holdout resampling.
```{r echo=TRUE, eval = FALSE}
# Custom function to split the full data into a training and a test subset.
twoSplit <- function(nonEventID=NULL, eventID=NULL,
                     tr=holdout[1], te=holdout[2], seed=NULL) {
    
    if(sum(tr, te)!=1) {
        stop("tr (training) and te (test) must sum up to 1.")
    }
    
    # Ensure that each training and each test subset across all resamplings resemble the full dataset. That is, the outcome in each training and test subset pair should have roughly 1.2% many outcome cases.
    
    # Size of training subset (80%) from participants without the outcome.
    trainN.non <- round(length(nonEventID)*tr, digits=0)
    # Size of test subset (20%) from participants without the outcome.
    testN.non <- round(length(nonEventID)*te, digits=0)
    
    # Size of training subset (80%) from participants with the outcome.
    trainN <- round(length(eventID)*tr, digits=0)
    # Size of test subset (20%) from participants with the outcome.
    testN <- round(length(eventID)*te, digits=0)
    
    # Make vector with training and test cases among participants without the ouctome (N = 4002). This vector has a neat order of 1s and 2s.
    nonEventSelect <- rep(1:2, times=c(trainN.non,
                                       testN.non))
    # Make vector with training and test cases among participants with the ouctome (N = 48). This vector has a neat order of 1s and 2s.
    eventSelect <- rep(1:2, times=c(trainN,
                                    testN))
    # Use the current seed to ensure perfect reproducibility.
    set.seed(seed)
    # Shake the neat vector nonEventSelect up. The 1s and 2s will then be scattered all over the place.
    nonEventSample <- sample(nonEventSelect)
    
    # Do the same thing to the vector eventSelect, what you just did to the vector nonEventSelect.
    set.seed(seed)
    eventSample <- sample(eventSelect)
    
    # Use the shaken up variables to randomly select the training cases.
    train <- c(nonEventID[nonEventSample==1],
               eventID[eventSample==1])
    
    # Use the shaken up variables to randomly select the test cases.
    test <- c(nonEventID[nonEventSample==2],
              eventID[eventSample==2])
    
    # Return as list the training and the test cases.
    return(list(train=train, test=test))
}
```

### Prepare outcome stratification.

Outcome stratification = The outcome event rate in the training and test subset shall always be as similar as possible as in the total sample.
```{r echo=TRUE, eval = FALSE}
# Extract which participants have not reported the outcome.
idNoCase <- which(data1$fsa==0)
# Extract which participants reported the outcome.
idCase <- which(data1$fsa==1)
```

### Run 100 distinct iterations of logistic regression cross-validated predictions.

Prediction performance results are collected after each iteration.
```{r echo=TRUE, eval = FALSE}
# Ensure reproducibility
set.seed(1)
# Sample 100 different seeds. Each seed will be used for one resampling iteration.
seeds20230324 <- sample(x=2:1984657, size=100)

# AUCs: AUROC and PRAUC (use precrec package)
AUCs <- c()
# confMatLs: confusion matrices collected in a list,
confMatLs <- list()
# Start for-loop (with 100 iterations). Runs 2-3 minutes.
for(i in 1:length(seeds20230324)) {
    
    print(i)
    
    # Make the resampling into training and test subsample
    testLs <- twoSplit(nonEventID = idNoCase,
                       eventID = idCase,
                       seed = seeds20230324[i])
    
    # train dataset 
    train <- data1[testLs$train,]
    # logistic regression applied to training dataset
    log_mod <- glm(fsa ~ ., family=binomial(link='logit'),data=train)
    # test dataset
    test <- data1[testLs$test,]
    # Apply coefficients from logistic regression model to test dataset.
    log_pred <- as.data.frame(predict(log_mod, test[,-length(test)], type='response'))
    # Result: Test dataset with observed outcome (column truth) and predicted probability (column prob) that the outcome was observed.
    dataTestset <- data.frame(truth=test$fsa, prob=log_pred[,1])
    
    # ----------------------------------
    # This section computes TP, FP, ..., sens, spec, ... prauc
    # ----------------------------------
    selectedThresholds <- c(0.5, 0.75, 1, 1.25, 1.5, 1.75, 2)/100
    trueClass <- factor(dataTestset$truth, levels = c("0", "1"))
    # Empty list, used to collect the confusion matrices in the for-loop.
    confMatLs_i <- list()
    # Inner for-loop which generates the confusion matrix for the current iteration AND for each of the seven thresholds.
    for(j in 1:length(selectedThresholds)) {
        predClass <-
            factor(dplyr::if_else(dataTestset$prob<selectedThresholds[j],0,1),
                   levels = c("0", "1"))
        tbl_j <- table(predClass, trueClass)
        
        sens <- tbl_j[2,2]/sum(tbl_j[,2]) # sensitivity
        spec <- tbl_j[1,1]/sum(tbl_j[,1]) # specificity
        ppv <- tbl_j[2,2]/sum(tbl_j[2,]) # positive predictive value
        npv <- tbl_j[1,1]/sum(tbl_j[1,]) # negative predictive value
        
        # Transform matrix to vector.
        tblVec_j <- as.vector(tbl_j)
        # Collect values in a tibble (= a data.frame)
        confMatLs_i[[j]] <- tibble::tibble(
            # TN True Negative, FP False Positive
            TN=tblVec_j[1], FP=tblVec_j[2],
            # FN False Negative, TP True Positive
            FN=tblVec_j[3], TP=tblVec_j[4],
            sens=sens, spec=spec, ppv=ppv, npv=npv
        )
    }
    # Bind the seven tibbles together
    confMatDf_i <- dplyr::bind_rows(confMatLs_i)
    # Add column thrsh (= threshold) in percent.
    confMatDf_i$thrsh <- selectedThresholds*100
    # Add column iter (iteration)
    confMatDf_i$iter <- i
    # Collect output for iteration i in list confMatLs.
    confMatLs[[i]] <- confMatDf_i
    
    # ----------------------------------
    # Compute auroc and prauc:
    aucs_i <- precrec::evalmod(scores = dataTestset$prob, labels = dataTestset$truth)
    # Add result to collecting vector AUCs.
    AUCs <- c(AUCs, precrec::auc(aucs_i)$aucs)
}
```

Quick impression of this single dataset (first 10 out of 700 rows).
```{r echo=TRUE, eval = FALSE}
confMatDf <- dplyr::bind_rows(confMatLs)
# Display rows 1-10 of confMatDf (confMat = confusion matrix; Df = data.frame)
confMatDf[1:10,]
#
#       TN    FP    FN    TP  sens  spec    ppv   npv thrsh  iter
#    <int> <int> <int> <int> <dbl> <dbl>  <dbl> <dbl> <dbl> <int>
#  1   360   440     1     9   0.9 0.45  0.0200 0.997  0.5      1
#  2   410   390     1     9   0.9 0.512 0.0226 0.998  0.75     1
#  3   502   298     2     8   0.8 0.628 0.0261 0.996  1        1
#  4   608   192     3     7   0.7 0.76  0.0352 0.995  1.25     1
#  5   688   112     5     5   0.5 0.86  0.0427 0.993  1.5      1
#  6   755    45     5     5   0.5 0.944 0.1    0.993  1.75     1
#  7   760    40     5     5   0.5 0.95  0.111  0.993  2        1
#  8   406   394     2     8   0.8 0.507 0.0199 0.995  0.5      2
#  9   497   303     2     8   0.8 0.621 0.0257 0.996  0.75     2
# 10   570   230     4     6   0.6 0.712 0.0254 0.993  1        2
```

**References**

Package citations, enter in R console: ?predictSuiattPsyCoLaus::predictSuiattPsyCoLaus

Then, on that help page, scroll down to References.