---
title: "E: Extract and display prediction performance results"
author: Marcel Miché
date: 2023-06-02
output:
  html_document:
    theme: yeti
    toc: false
vignette: >
  %\VignetteIndexEntry{E: Extract and display prediction performance results}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## All code to extract prediction results from logistic regression and from classification and regression trees (CART).

*Note* that all computations from vignettes C and D must have been finished, before continuing with the below code.

## Inspect the collected prediction performances.

Both, logistic regression and CART were run 700 times (100 cross-validations for each of the seven threshold probabilities/harm-to-benefit ratio). Each time the true positives and the false positives were recorded, among other results.

Since each of 700 cross-validations consisted of a sample size of 810, of which 10 subjects developed the outcome, the net benefit of the treat all scenario across each of the 7 selected thresholds remained constant. This is how the net benefit for the treat all scenario is computed (see also the other supplementary material, which contains a detailed explanation of the decision curve analysis, from which net benefit is derived).

```{r echo=TRUE, eval = TRUE}
# hbr: harm-benefit ratio
hbr <- function(x) {
    return(x/(1-x))
}
hbrVec <- hbr(c(.005, .0075, .01, .0125, .015, .0175, .02))
# Outcome incidence in each test subset
inc <- 10/810
# Compute net benefit for the treat all scenario
nbTreatAll <- inc - (1-inc)*hbrVec
# Display harm-to-benefit ratio, e.g., the first is 1/199 = 0.00738.
cbind(nbTreatAll)
```