---
title: "E: Compute and display clinical utility results"
author: Marcel Miché
date: 2023-07-31
output:
  html_document:
    theme: yeti
    toc: false
vignette: >
  %\VignetteIndexEntry{E: Compute and display clinical utility results}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## All code to compute and present clinical utility results for logistic regression and for classification and regression trees (CART).

**Note** that all computations from vignettes C and D must have been finished, before continuing with the below code.

## Inspect the collected prediction performances.

Both, logistic regression and CART were run 700 times (100 cross-validations for each of the seven threshold probabilities/harm-to-benefit ratio). Each time the true positives and the false positives were recorded, among other results.

Since each of 700 cross-validations consisted of a sample size of 810, of which 10 subjects developed the outcome, the net benefit of the treat all scenario across each of the 7 selected thresholds remained constant. This is how the net benefit for the treat all scenario is computed (see also the other supplementary material, which contains a detailed explanation of the decision curve analysis, from which net benefit is derived).

```{r echo=TRUE, eval = TRUE}
# Custom function to compute harm-to-benefit ratio (hbr)
hbr <- function(x) {
    return(x/(1-x))
}
# FPwt = false positive weight; 1/199 = 0.005025126, etc.
(FPwt <- hbr(c(.005, .0075, .01, .0125, .015, .0175, .02)))
# Outcome incidence in each of the 700 test subsets
inc <- 10/810
# Compute net benefit for the treat all scenario
nbTreatAll <- inc - FPwt*(1-inc)
# Display harm-to-benefit ratio, e.g., the first is 1/199 = 0.00738.
cbind(nbTreatAll)
```

## The seven threshold probabilities correspond to these harm-to-benefit ratios.
```{r echo=TRUE, eval = TRUE}
# probThresh = probability thresholds; htb = harm-to-benefit ratio (rounded to three decimals); FPwt = weight by which false positives get weighted.
data.frame(
    probThresh=c(.005, .0075, .01, .0125, .015, .0175, .02),
    htb=c("1:199", "1:132.333", "1:99", "1:79", "1:65.667", "1:56.143", "1:49"),
    FPwt=FPwt)
```

## Custom function to compute the net benefit of the prediction model
```{r echo=TRUE, eval = FALSE}
# tp = true positives, fp = false positives, FPwt = false positives weight.
nbModFun <- function(tp=NULL, fp=NULL, FPwt=NULL) {
    return((tp - FPwt*fp)/810)
}
```

## Custom function to compute the clinical utility results for a classification prediction model.

**Note** The variable 'level' with values 1-7 refers to the seven selected threshold probabilities (level = 1 = 0.5%, ..., level = 7 = 2%).
```{r echo=TRUE, eval = FALSE}
# Argument confMatDf = confusion matrix data.frame. That is, confMatDf contains 10 columns, 8 of which comprise the confusion matrix or are directly computed on the basis of the confusion matrix, e.g., sensitivity.
computeResults <- function(confMatDf=NULL) {
    # Append a distinct column that shows the seven unique levels of threshold probabilities (logreg) or harm-to-benefit ratios (CART).
    confMatDf$level <- rep(1:7, times=100)
    # Append the FPwt to confMatDf.
    confMatDf$FPwt <- rep(FPwt, times=100)
    # Append the treat all net benefit to confMatDf.
    confMatDf$nbTreatAll <- rep(nbTreatAll, times=100)
    # Append the treat none net benefit to confMatDf.
    confMatDf$nbTreatNone <- rep(0, times=nrow(confMatDf))
    # Compute and append the prediction model net benefit to confMat. Use custom function nbModFun for this.
    confMatDf$nbModel <- nbModFun(tp=confMatDf$TP, fp=confMatDf$FP, FPwt=confMatDf$FPwt)
    # deltaNb: Difference between net benefit of the prediction model and net benefit of the next best contender (e.g., treat all or treat none).
    confMatDf$deltaNb <-
        # Column 'level' in confMatDf represents the thresholds (for logreg) or FPwt (for CART).
        dplyr::if_else(confMatDf$level <= 3,
                       confMatDf$nbModel - confMatDf$nbTreatAll,
                       confMatDf$nbModel)
    return(confMatDf)
}
```

**Note**: Delta net benefit, in our study, is defined as the result from comparing the increase in true positives of the prediction model and:

* treat all, for threshold probabilities 0.5%, 0.75%, and 1% (which are all below the outcome rate of 1.23% in the test dataset).
* treat none, for threshold probabilities 1.25%, 1.5%, 1.75%, and 2% (which are all above the outcome rate of 1.23% in the test dataset).

## Apply this custom function to the 100 cross-validated predictions

### Logistic regression
```{r echo=TRUE, eval = FALSE}
# Apply custom function computeResults to the logistic regression output.
logregCompleted <- computeResults(predictSuiattPsyCoLaus::logreg700)
```

### CART
```{r echo=TRUE, eval = FALSE}
# Apply custom function computeResults to the CART output.
CARTcompleted <- computeResults(predictSuiattPsyCoLaus::CART700)
```

## Display the summarized results

For each probability threshold (or harm-to-benefit ratio), compute median, maximum, and minimum net benefit.
```{r echo=TRUE, eval = FALSE}
# Logistic regression
(logregNB <- logregCompleted %>%
    group_by(level) %>%
     summarise(
         Median=median(nbModel),
         Max=max(nbModel),
         Min=min(nbModel)
     ))
# Output in R console
#   level  Median     Max       Min
#   <int>   <dbl>   <dbl>     <dbl>
# 1     1 0.00866 0.0100   0.00498 
# 2     2 0.00777 0.00953  0.00444 
# 3     3 0.00604 0.00933  0.00228 
# 4     4 0.00459 0.00925  0.000563
# 5     5 0.00371 0.00826  0.000401
# 6     6 0.00363 0.00777 -0.000151
# 7     7 0.00398 0.00781  0.000252

# CART (results shown in figure 1 of the main document)
(cartNB <- CARTcompleted %>%
    group_by(level) %>%
        summarise(
            Median=median(nbModel),
            Max=max(nbModel),
            Min=min(nbModel)
        ))
# Output in R console
#   level  Median     Max      Min
#   <int>   <dbl>   <dbl>    <dbl>
# 1     1 0.00543 0.00993 0.00139 
# 2     2 0.00559 0.00930 0.00201 
# 3     3 0.00494 0.00868 0.00142 
# 4     4 0.00413 0.00820 0.000906
# 5     5 0.00342 0.00802 0.000721
# 6     6 0.00318 0.00814 0.000424
# 7     7 0.00277 0.00685 0.000126
```

## Prepare output to plot the (median) decision curves
```{r echo=TRUE, eval = FALSE}
dcaDf <- tibble(
    label = factor(
        rep(c("Treat all", "Treat none", "Logistic regression", "CART"), each=8),
        levels = c("Logistic regression", "CART", "Treat all", "Treat none")),
    threshold = rep(c(0, .005, .0075, .01, .0125, .015, .0175, .02), times=4),
    # Net benefit of:
    # Treat all, treat none, logistic regression model, CART model.
    # inc = outcome incidence (10/810)
    net_benefit = c(inc, nbTreatAll,
                    rep(0, times=8),
                    inc, logregNB$Median,
                    inc, cartNB$Median)
)
```

Output in R console
```{r echo=TRUE, eval = FALSE}
print(dcaDf, n=nrow(dcaDf))
   label               threshold net_benefit
   <fct>                   <dbl>       <dbl>
 1 Treat all              0         0.0123  
 2 Treat all              0.005     0.00738 
 3 Treat all              0.0075    0.00488 
 4 Treat all              0.01      0.00237 
 5 Treat all              0.0125   -0.000156
 6 Treat all              0.015    -0.00269 
 7 Treat all              0.0175   -0.00525 
 8 Treat all              0.02     -0.00781 
 9 Treat none             0         0       
10 Treat none             0.005     0       
11 Treat none             0.0075    0       
12 Treat none             0.01      0       
13 Treat none             0.0125    0       
14 Treat none             0.015     0       
15 Treat none             0.0175    0       
16 Treat none             0.02      0       
17 Logistic regression    0         0.0123  
18 Logistic regression    0.005     0.00866 
19 Logistic regression    0.0075    0.00777 
20 Logistic regression    0.01      0.00604 
21 Logistic regression    0.0125    0.00459 
22 Logistic regression    0.015     0.00371 
23 Logistic regression    0.0175    0.00363 
24 Logistic regression    0.02      0.00398 
25 CART                   0         0.0123  
26 CART                   0.005     0.00543 
27 CART                   0.0075    0.00559 
28 CART                   0.01      0.00494 
29 CART                   0.0125    0.00413 
30 CART                   0.015     0.00342 
31 CART                   0.0175    0.00318 
32 CART                   0.02      0.00277
```

## Plot the (median) decision curves

Median is in paranthesis because this refers only to the net benefit of logistic regression and CART. That is, net benefit for treat all and treat none remains constant across all 100 cross-validations (because in each cross-validation subsample, there are exactly 10 outcome cases among 810 individuals).
```{r echo=TRUE, eval = FALSE}
# Custom function to convert threshold probability to harm-to-benefit ratio.
htbPlot <- function(x) paste0("1:", round((1-x)/x, digits=1))

# Generate figure 1 of the main document:
useColor <- c("Treat all" = "black", "Treat none" = "black",
              "Logistic regression" = "black", "CART" = "black")

ggplot(data=dcaDf, aes(x=threshold, y=net_benefit, colour=label)) +
    geom_line(aes(linetype=label), linewidth=1) +
    labs(color=NULL) +
    coord_cartesian(ylim=c(-.0025, .015)) +
    # With 0% and 1:Inf
    scale_x_continuous(
        breaks = seq(0, 0.02, by=.0025)[-2],
        labels = c("0%", "0.5%", "0.75%", "1%", "1.25%", "1.5%", "1.75%", "2%"),
        sec.axis = dup_axis(name="Harm-to-benefit ratio", labels=htbPlot)) +
    
    scale_colour_manual(values = useColor) +
    
    scale_linetype_manual(values = c("solid", "dotdash", "dashed", "dotted")) +
    
    guides(colour="none") +
    
    ylab(label="Net benefit") +
    theme(
        panel.background = element_blank(),
        axis.text.x=element_text(size=16),
        axis.title.x=element_text(size=16),
        axis.text.y=element_text(size=16),
        axis.title.y = element_text(size=16),
        panel.border = element_rect(color="black", fill=NA),
        legend.text = element_text(size=14),
        legend.position = "top",
        legend.title = element_blank()) +
    labs(x="Threshold probability")
```

**Note.** The plot itself is shown in the main article and/or the supplementary material 1. You can generate the plot yourself by using the R script 'E_DisplayResults', which is part of this supplementary material 2 (R package, see folder 'rscriptsVignettes' on the GitHub page).

## Compute delta net benefit and present the summarized results

For each probability threshold (or harm-to-benefit ratio), compute median, maximum, and minimum delta net benefit.

```{r echo=TRUE, eval = FALSE}
# Logistic regression
# First, remove the 18 models with a negative delta net benefit.
(logregDeltaNB <-
logregCompleted[logregCompleted$deltaNb>=0,] %>%
    group_by(level) %>%
    summarise(
        Median=median(deltaNb),
        Max=max(deltaNb),
        Min=min(deltaNb)
    ))
# Output in R console
#   level  Median     Max       Min
#   <int>   <dbl>   <dbl>     <dbl>
# 1     1 0.00140 0.00266 0.0000496
# 2     2 0.00290 0.00465 0.000131 
# 3     3 0.00370 0.00696 0.000200 
# 4     4 0.00459 0.00925 0.000563 
# 5     5 0.00371 0.00826 0.000401 
# 6     6 0.00364 0.00777 0.000531 
# 7     7 0.00398 0.00781 0.000252

# CART
# First, remove the 119 models with a negative delta net benefit.
(cartDeltaNB <-
CARTcompleted[CARTcompleted$deltaNb>=0,] %>%
    group_by(level) %>%
        summarise(
            Median=median(deltaNb),
            Max=max(deltaNb),
            Min=min(deltaNb)
        ))
# Output in R console
#   level   Median     Max      Min
#   <int>    <dbl>   <dbl>    <dbl>
# 1     1 0.000341 0.00254 8.67e-19
# 2     2 0.00140  0.00442 2.18e- 5
# 3     3 0.00266  0.00631 1.37e- 4
# 4     4 0.00413  0.00820 9.06e- 4
# 5     5 0.00342  0.00802 7.21e- 4
# 6     6 0.00318  0.00814 4.24e- 4
# 7     7 0.00277  0.00685 1.26e- 4
```

## Display the potentially harmful models (i.e., models with a negative delta net benefit)
```{r echo=TRUE, eval = FALSE}
# Logistic regression (results shown in figure 1 of the main document)
addmargins(table(logregCompleted[logregCompleted$deltaNb<0,"level"]))
# Output in R console
#  1   2   3   6 Sum 
# 14   2   1   1  18

# CART (results shown in figure 1 of the main document)
addmargins(table(CARTcompleted[CARTcompleted$deltaNb<0,"level"]))
# Output in R console
#  1   2   3 Sum 
# 75  38   6 119
```

**References**

Package citations, enter in R console: ?predictSuiattPsyCoLaus::predictSuiattPsyCoLaus

Then, on that help page, scroll down to References.