---
title: "G: Conduct and display result of CART sensitivity analysis"
author: Marcel Miché
date: 2023-06-02
output:
  html_document:
    theme: yeti
    toc: false
vignette: >
  %\VignetteIndexEntry{G: Conduct and display result of CART sensitivity analysis}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Same starting code as in vignette E
```{r echo=TRUE, eval = TRUE}
# Custom function to compute harm-to-benefit ratio (hbr)
hbr <- function(x) {
    return(x/(1-x))
}
# FPwt = false positive weight; 1/199 = 0.005025126, etc.
(FPwt <- hbr(c(.005, .0075, .01, .0125, .015, .0175, .02)))
# Outcome incidence in each of the 700 test subsets
inc <- 10/810
# Compute net benefit for the treat all scenario
nbTreatAll <- inc - FPwt*(1-inc)
# Display harm-to-benefit ratio, e.g., the first is 1/199 = 0.00738.
cbind(nbTreatAll)

# probThresh = probability thresholds; htb = harm-to-benefit ratio (rounded to three decimals); FPwt = weight by which false positives get weighted.
data.frame(
    probThresh=c(.005, .0075, .01, .0125, .015, .0175, .02),
    htb=c("1:199", "1:132.333", "1:99", "1:79", "1:65.667", "1:56.143", "1:49"),
    FPwt=FPwt)
```


```{r echo=TRUE, eval = FALSE}
# tp = true positives, fp = false positives, FPwt = false positives weight.
nbModFun <- function(tp=NULL, fp=NULL, FPwt=NULL) {
    return((tp - FPwt*fp)/810)
}
# Argument confMatDf = confusion matrix data.frame. That is, confMatDf contains 10 columns, 8 of which comprise the confusion matrix or are directly computed on the basis of the confusion matrix.
computeResults <- function(confMatDf=NULL) {
    # Append a distinct column that shows the seven unique levels of threshold probabilities (logreg) or harm-to-benefit ratios (CART).
    confMatDf$level <- rep(1:7, times=100)
    # Append the FPwt to confMatDf.
    confMatDf$FPwt <- rep(FPwt, times=100)
    # Append the treat all net benefit to confMatDf.
    confMatDf$nbTreatAll <- rep(nbTreatAll, times=100)
    # Append the treat none net benefit to confMatDf.
    confMatDf$nbTreatNone <- rep(0, times=nrow(confMatDf))
    # Compute and append the prediction model net benefit to confMat. Use custom function nbModFun for this.
    confMatDf$nbModel <- nbModFun(tp=confMatDf$TP, fp=confMatDf$FP, FPwt=confMatDf$FPwt)
    # deltaNb: Difference between net benefit of the prediction model and net benefit of the next best contender (e.g., treat all or treat none).
    confMatDf$deltaNb <-
        # Column 'level' in confMatDf represents the thresholds (for logreg) or FPwt (for CART).
        dplyr::if_else(confMatDf$level <= 3,
                       confMatDf$nbModel - confMatDf$nbTreatAll,
                       confMatDf$nbModel)
    return(confMatDf)
}
# Apply custom function computeResults to the logistic regression output.
logregCompleted <- computeResults(predictSuiattPsyCoLaus::logreg700)

# Apply custom function computeResults to the CART output.
CARTcompleted <- computeResults(predictSuiattPsyCoLaus::CART700)
```

## Starting CART sensitivity analysis

### First, apply custom function 'computeResults' to every of the five CART pruned results.

That is: cp = 0 (no pruning), cp = .01, cp = .02, cp = .03, cp = .04, cp = .05.
*Note* cp is the function argument of CART (see function rpart in the rpart package), which executes the pruning (= recursively snipping off the least important splits of the CART decision tree).
```{r echo=TRUE, eval = FALSE}
CARTPrunedLs <- lapply(predictSuiattPsyCoLaus::CART700Pruned,
                       FUN = computeResults)
```

## Custom function 'correspond'

Since the median net benefit is computed across all 100 cross-validations for each of the seven threshold probabilities, this computed median net benefit may not precisely correspond to any of the 100 cross-validated net benefits. Therefore, this 'correspond' function extracts the closest net benefit values. Maximum and minimum net benefits must precisely correspond.

```{r echo=TRUE, eval = FALSE}
correspond <- function(data=NULL) {
    
    # For the given 100 cross-validations (logistic regression or CART), compute median, minimum, and maximum net benefit for each of the seven levels (level = threshold probability for logistic regression or harm-to-benefit ratio for CART).
    medMaxMinDf <-
        data %>% group_by(level) %>%
        summarise(
            Median=median(nbModel),
            Max=max(nbModel),
            Min=min(nbModel)
        )
    # outVec: Vector that is used in the inner for-loop, to assign the correct name, either Median, Minimum, or Maximum.
    outVec <- c(NA, "Median", "Maximum", "Minimum")
    # Empty vectors to collect the results that will be returned at the end of the outer for-loop.
    name <- level <- medMaxMinIdx <- c()
    # Outer for-loop. lvl = column 'level' in function argument data.
    # lvl <- 1; dfCols <- 2
    for(lvl in 1:7) {
        # Inner for-loop. It iterates across the columns 2, 3, and 4, of medMaxMinDf (see above).
        for(dfCols in 2:4) {
            
            # Column 2 of medMaxMinDf contains the median net benefit.
            if(dfCols==2) {
                
                # If there is a precise match across the 100 cross-validated net benefits, use that matching net benefit.
                if(any(logregCompleted[data$level==lvl,"nbModel"][[1]] == medMaxMinDf[medMaxMinDf$level==lvl,"Median"][[1]])) {
                    # Find exact match.
                    idxMedian <- which(data[data$level==lvl,"nbModel"][[1]] == medMaxMinDf[medMaxMinDf$level==lvl,"Median"][[1]])
                    # Assign name "Median" as often as there are exact matches.
                    name <- c(name, rep(outVec[dfCols], times=length(idxMedian)))
                    # Assign level (a value between 1 and 7) as often as there are exact matches.
                    level <- c(level, rep(lvl, times=length(idxMedian)))
                    # Collect the exact matching net benefit(s).
                    medMaxMinIdx <- c(medMaxMinIdx, which(data$level==lvl)[idxMedian])
                    
                    # Else: Use the next closest net benefit across the 100 cross-validated net benefits.
                } else {
                    # Store vector of 100 net benefits; multiply by 100, to get higher precision in variable absDiffVec (below).
                    nb100 <- data[data$level==lvl,"nbModel"][[1]] * 100
                    # Store single median net benefit from medMaxMinDf (reference net benefit), also multiply by 100.
                    nbReference <- medMaxMinDf[medMaxMinDf$level==lvl,"Median"][[1]] * 100
                    # Find closest value across the 100 cross-validated net benefits.
                    absDiffVec <- abs(nb100 - nbReference) # abs = absolute values.
                    # Find all occurrences across the 100 cross-validated net benefits that are near this closest value.
                    idxMedian <- which(absDiffVec == min(absDiffVec))
                    # Assign name "Median" as often as there are closest matches.
                    name <- c(name, rep(outVec[dfCols], times=length(idxMedian)))
                    # Assign level (a value between 1 and 7) as often as there are closest matches.
                    level <- c(level, rep(lvl, times=length(idxMedian)))
                    # Collect the closest matching net benefit(s).
                    medMaxMinIdx <- c(medMaxMinIdx, which(data$level==lvl)[idxMedian])
                }
                # Remaining two columns 3 and 4: Max and Min in medMaxMinDf
            } else {
                # Find exact match.
                idxMaxMin <- which(data[data$level==lvl,"nbModel"][[1]] == medMaxMinDf[medMaxMinDf$level==lvl, dfCols][[1]])
                # Assign column name as often as there are exact matches.
                name <- c(name, rep(outVec[dfCols], times=length(idxMaxMin)))
                # Assign level (a value between 1 and 7) as often as there are exact matches.
                level <- c(level, rep(lvl, times=length(idxMaxMin)))
                # Collect the exact matching net benefit(s).
                medMaxMinIdx <- c(medMaxMinIdx, which(data$level==lvl)[idxMaxMin])
            }
        }
    }
    return(tibble(name, level, medMaxMinIdx))
}
```

It may be possible to have more than one net benefit that matches the median, the maximum, or the minimum net benefit across all 100 cross-validations. Therefore, extract unique median, maximum, and minimum net benefit with this custom function.

```{r echo=TRUE, eval = FALSE}
correspondUnique <- function(correspondDf=NULL) {
    idx_i <- c()
    for(i in 1:7) {
        correspondDf_i <- correspondDf[correspondDf[,"level"]==i,]
        idx_i <- c(idx_i, !duplicated(correspondDf_i[,"name"]))
    }
    return(correspondDf[idx_i,])
}
```

## Apply the custom functions

### Logistic regression

```{r echo=TRUE, eval = FALSE}
# Extract corresponding row indices (values between 1 and 700)
logregCorrespondDf <- correspond(data=logregCompleted)
# Apply extracted indices
logregCompletedMedMaxMin <- logregCompleted[logregCorrespondDf$medMaxMinIdx,]
logregCompletedMedMaxMin$name <- logregCorrespondDf$name
# Reduce to unique median, maximum, and minimum net benefit
logregCompletedMedMaxMinUnique <- correspondUnique(logregCompletedMedMaxMin)
print(logregCompletedMedMaxMinUnique[,c("name", "iter", "FP", "TP", "level", "FPwt", "nbModel", "deltaNb")], n=21)
# Output in R console
#    name     iter    FP    TP level    FPwt   nbModel    deltaNb
#    <chr>   <int> <int> <int> <int>   <dbl>     <dbl>      <dbl>
#  1 Median     26   395     9     1 0.00503  0.00866   0.00128  
#  2 Maximum    90   371    10     1 0.00503  0.0100    0.00266  
#  3 Minimum    67   391     6     1 0.00503  0.00498  -0.00240  
#  4 Median      4   360     9     2 0.00756  0.00775   0.00287  
#  5 Maximum    87   302    10     2 0.00756  0.00953   0.00465  
#  6 Minimum    67   318     6     2 0.00756  0.00444  -0.000442 
#  7 Median     88   206     7     3 0.0101   0.00607   0.00370  
#  8 Maximum    69   242    10     3 0.0101   0.00933   0.00696  
#  9 Minimum    96   213     4     3 0.0101   0.00228  -0.0000873
# 10 Median     11   178     6     4 0.0127   0.00463   0.00463  
# 11 Maximum    97   198    10     4 0.0127   0.00925   0.00925  
# 12 Minimum    39   201     3     4 0.0127   0.000563  0.000563 
# 13 Median     13   131     5     5 0.0152   0.00371   0.00371  
# 14 Maximum    51    86     8     5 0.0152   0.00826   0.00826  
# 15 Minimum     2   110     2     5 0.0152   0.000401  0.000401 
# 16 Median      6    59     4     6 0.0178   0.00364   0.00364  
# 17 Maximum    77    96     8     6 0.0178   0.00777   0.00777  
# 18 Minimum     2    63     1     6 0.0178  -0.000151 -0.000151 
# 19 Median      6    38     4     7 0.0204   0.00398   0.00398  
# 20 Maximum    16    33     7     7 0.0204   0.00781   0.00781  
# 21 Minimum     2    39     1     7 0.0204   0.000252  0.000252
```

### CART (default, i.e., without using the cp parameter for pruning)

```{r echo=TRUE, eval = FALSE}
# Extract corresponding row indices (values between 1 and 700)
cartCorrespondDf <- correspond(data=CARTcompleted)
# Apply extracted indices
CARTcompletedMedMaxMin <- CARTcompleted[cartCorrespondDf$medMaxMinIdx,]
CARTcompletedMedMaxMin$name <- cartCorrespondDf$name
# Reduce to unique median, maximum, and minimum net benefit
CARTcompletedMedMaxMinUnique <- correspondUnique(CARTcompletedMedMaxMin)
print(CARTcompletedMedMaxMinUnique[,c("name", "iter", "FP", "TP", "level", "FPwt", "nbModel", "deltaNb")], n=21)
# Output in R console
#    name     iter    FP    TP level    FPwt  nbModel   deltaNb
#    <chr>   <dbl> <dbl> <dbl> <int>   <dbl>    <dbl>     <dbl>
#  1 Median      9   120     5     1 0.00503 0.00543  -0.00195 
#  2 Maximum    55   191     9     1 0.00503 0.00993   0.00254 
#  3 Minimum    22   174     2     1 0.00503 0.00139  -0.00599 
#  4 Median      1   197     6     2 0.00756 0.00557   0.000687
#  5 Maximum    55   194     9     2 0.00756 0.00930   0.00442 
#  6 Minimum    22   182     3     2 0.00756 0.00201  -0.00288 
#  7 Median     76   197     6     3 0.0101  0.00495   0.00258 
#  8 Maximum    55   195     9     3 0.0101  0.00868   0.00631 
#  9 Minimum    98    84     2     3 0.0101  0.00142  -0.000948
# 10 Median     32   132     5     4 0.0127  0.00411   0.00411 
# 11 Maximum    55   186     9     4 0.0127  0.00820   0.00820 
# 12 Minimum    22   179     3     4 0.0127  0.000906  0.000906
# 13 Median      3    81     4     5 0.0152  0.00342   0.00342 
# 14 Maximum    42    99     8     5 0.0152  0.00802   0.00802 
# 15 Minimum    61    93     2     5 0.0152  0.000721  0.000721
# 16 Median      6    80     4     6 0.0178  0.00318   0.00318 
# 17 Maximum    42    79     8     6 0.0178  0.00814   0.00814 
# 18 Minimum    61    93     2     6 0.0178  0.000424  0.000424
# 19 Maximum    24    71     7     7 0.0204  0.00685   0.00685 
# 20 Minimum    61    93     2     7 0.0204  0.000126  0.000126
```

### CART (pruning: No pruning, cp = .01, cp = .02, cp = .03, cp = .04, cp = .05)

```{r echo=TRUE, eval = FALSE}
# Extract corresponding row indices (values between 1 and 700)
cartCorrespondPrunedDf <- lapply(CARTPrunedLs, FUN=correspond)
# Apply extracted indices
CARTcompletedMedMaxMinPrunedLs <- list()
for(i in 1:length(CARTPrunedLs)) {
    
    CARTPrunedMedMaxMin_i <- CARTPrunedLs[[i]][cartCorrespondPrunedDf[[i]]$medMaxMinIdx,]
    CARTPrunedMedMaxMin_i$name <- cartCorrespondPrunedDf[[i]]$name
    
    CARTcompletedMedMaxMinPrunedLs[[i]] <- CARTPrunedMedMaxMin_i
    
}
# Reduce to unique median, maximum, and minimum net benefit
CARTcompletedMedMaxMinPrunedLsUnique <- lapply(CARTcompletedMedMaxMinPrunedLs,
                                               FUN=correspondUnique)
print(CARTcompletedMedMaxMinPrunedLsUnique[[3]][,c("name", "iter", "FP", "TP", "level", "FPwt", "nbModel", "deltaNb")], n=21)
# Output in R console (exemplary for cp = .02, third element in list)
#    name     iter    FP    TP level    FPwt  nbModel   deltaNb
#    <chr>   <int> <int> <int> <int>   <dbl>    <dbl>     <dbl>
#  1 Median     23   310     7     1 0.00503 0.00672  -0.000664
#  2 Maximum    55   275    10     1 0.00503 0.0106    0.00326 
#  3 Minimum    44   152     3     1 0.00503 0.00276  -0.00462 
#  4 Median     56   294     7     2 0.00756 0.00590   0.00102 
#  5 Maximum    55   276    10     2 0.00756 0.00977   0.00489 
#  6 Minimum    82   334     4     2 0.00756 0.00182  -0.00306 
#  7 Median     18   255     7     3 0.0101  0.00546   0.00309 
#  8 Maximum     4   182     9     3 0.0101  0.00884   0.00647 
#  9 Minimum    82   201     3     3 0.0101  0.00120  -0.00117 
# 10 Median     37   154     6     4 0.0127  0.00500   0.00500 
# 11 Maximum     4   168     9     4 0.0127  0.00849   0.00849 
# 12 Minimum    22   166     3     4 0.0127  0.00111   0.00111 
# 13 Median     46   171     6     5 0.0152  0.00419   0.00419 
# 14 Maximum     4   171     9     5 0.0152  0.00790   0.00790 
# 15 Minimum    22   166     3     5 0.0152  0.000583  0.000583
# 16 Median      5   164     6     6 0.0178  0.00380   0.00380 
# 17 Maximum     4   171     9     6 0.0178  0.00735   0.00735 
# 18 Minimum     9    32     1     6 0.0178  0.000531  0.000531
# 19 Median     80    44     4     7 0.0204  0.00383   0.00383 
# 20 Maximum   100   106     8     7 0.0204  0.00721   0.00721 
# 21 Minimum     9    32     1     7 0.0204  0.000428  0.000428
```

## Prepare plotting the results of the CART sensitivity analysis

### Put summary results into a list.

```{r echo=TRUE, eval = FALSE}
# logregSmry to be used in CART sensitivity analysis plot of all decision curves.
(logregSmry <- logregCompleted %>%
    group_by(level) %>%
    summarise(
        Median=median(nbModel),
        Max=max(nbModel),
        Min=min(nbModel)
    ))

# CARTsmry to be used in CART sensitivity analysis plot of all decision curves.
(CARTsmry <- CARTcompleted %>%
    group_by(level) %>%
    summarise(
        Median=median(nbModel),
        Max=max(nbModel),
        Min=min(nbModel)
    ))

# cartCorrespondPrunedSmryDf to be used in CART sensitivity analysis plot of all decision curves.
(cartCorrespondPrunedSmryDf <- lapply(CARTPrunedLs, function(x) {
    
    x %>% group_by(level) %>%
        summarise(
            Median=median(nbModel),
            Max=max(nbModel),
            Min=min(nbModel)
        )
    
}))

dcaLs <- list(lgrg=logregSmry,
              cart=CARTsmry,
              cart02=cartCorrespondPrunedSmryDf[["cp_0.02"]],
              cart03=cartCorrespondPrunedSmryDf[["cp_0.03"]],
              cart04=cartCorrespondPrunedSmryDf[["cp_0.04"]],
              cart05=cartCorrespondPrunedSmryDf[["cp_0.05"]])
names(dcaLs) <- c("Logistic regression", "CART", "CARTcp02", "CARTcp03", "CARTcp04", "CARTcp05")
```

Output of dcaLs in R console

```{r echo=TRUE, eval = FALSE}
$`Logistic regression`
# A tibble: 7 × 4
  level  Median     Max       Min
  <int>   <dbl>   <dbl>     <dbl>
1     1 0.00866 0.0100   0.00498 
2     2 0.00777 0.00953  0.00444 
3     3 0.00604 0.00933  0.00228 
4     4 0.00459 0.00925  0.000563
5     5 0.00371 0.00826  0.000401
6     6 0.00363 0.00777 -0.000151
7     7 0.00398 0.00781  0.000252

$CART
# A tibble: 7 × 4
  level  Median     Max      Min
  <int>   <dbl>   <dbl>    <dbl>
1     1 0.00543 0.00993 0.00139 
2     2 0.00559 0.00930 0.00201 
3     3 0.00494 0.00868 0.00142 
4     4 0.00413 0.00820 0.000906
5     5 0.00342 0.00802 0.000721
6     6 0.00318 0.00814 0.000424
7     7 0.00277 0.00685 0.000126

$CARTcp02
# A tibble: 7 × 4
  level  Median     Max      Min
  <int>   <dbl>   <dbl>    <dbl>
1     1 0.00672 0.0106  0.00276 
2     2 0.00596 0.00977 0.00182 
3     3 0.00542 0.00884 0.00120 
4     4 0.00498 0.00849 0.00111 
5     5 0.00416 0.00790 0.000583
6     6 0.00380 0.00735 0.000531
7     7 0.00383 0.00721 0.000428

$CARTcp03
# A tibble: 7 × 4
  level  Median     Max      Min
  <int>   <dbl>   <dbl>    <dbl>
1     1 0.00694 0.0102  0.00346 
2     2 0.00606 0.00984 0.00214 
3     3 0.00546 0.00899 0.000836
4     4 0.00492 0.00849 0.000734
5     5 0.00421 0.00825 0.000633
6     6 0.00404 0.00892 0.000531
7     7 0.00403 0.00915 0.000428

$CARTcp04
# A tibble: 7 × 4
  level  Median     Max      Min
  <int>   <dbl>   <dbl>    <dbl>
1     1 0.00754 0.00959 0.00394 
2     2 0.00631 0.00889 0.00246 
3     3 0.00559 0.00899 0.000836
4     4 0.00440 0.00736 0.000734
5     5 0.00422 0.00833 0.000633
6     6 0.00415 0.00924 0.000531
7     7 0.00404 0.00915 0.000428

$CARTcp05
# A tibble: 7 × 4
  level  Median     Max      Min
  <int>   <dbl>   <dbl>    <dbl>
1     1 0.00818 0.00959 0.00394 
2     2 0.00684 0.00889 0.00246 
3     3 0.00579 0.00814 0.000836
4     4 0.00436 0.00722 0.000734
5     5 0.00426 0.00833 0.000633
6     6 0.00415 0.00924 0.000531
7     7 0.00404 0.00915 0.000428
```

Custom function to produce a single data.frame that can be used for plotting the results of the CART sensitivity analysis.

```{r echo=TRUE, eval = FALSE}
# hbr: Custom function to compute the harm-benefit ratio; x = a single threshold probability.
hbr <- function(x) {
    if(any(x < 0) | any(x > 1)) {
        stop("Threshold probabilities must lie between 0 and 1.")
    }
    return(x/(1-x))
}

# Custom function to generate the data that is needed to plot the decision curves.
makeDCADf <- function(dataLs=NULL, colName="Median") {
    # FPwt = false positive weight; 1/199 = 0.005025126, etc.
    FPwt <- hbr(c(.005, .0075, .01, .0125, .015, .0175, .02))
    # Outcome incidence in each of the 700 test subsets
    inc <- 10/810
    # Seven threshold probabilities, in addition to the threshold 0.
    thrsh <- c(0, .005, .0075, .01, .0125, .015, .0175, .02)
    # Net benefit of treat all
    nbTreatAll <- c(inc, inc - FPwt*(1-inc))
    # Net benefit of treat none
    nbTreatNone <- rep(0, times=length(nbTreatAll))
    # Labels of the clinical decision scenarios.
    label <- rep(c("Treat all", "Treat none"), each=8)
    # Empty vector to collect the net benefit of the prediction models.
    nbModel <- c()
    for(i in 1:length(dataLs)) {
        # Collect net benefit from the summary table.
        nbModel <- c(nbModel, inc, dataLs[[i]][,colName][[1]])
        # Add the current model's name to the label vector.
        label <- c(label, rep(names(dataLs)[i], times=8))
    }
    # Make vector with the overall eight threshold probabilities.
    threshold <- rep(thrsh, times=sum(2, length(dataLs)))
    
    return(
        tibble(
            label=forcats::as_factor(label),
            threshold=threshold,
            net_benefit=c(nbTreatAll, nbTreatNone, nbModel)
        )
    )
}

# Use either Min (minimum), Max (maximum), or Median for argument colName.
# The selected colName will then be plotted in the decision curves plot.
dcaDf <- makeDCADf(dataLs = dcaLs, colName = "Median")
```

## Plot the results of the CART sensitivity analysis

```{r echo=TRUE, eval = FALSE}
# Select colors, for instance, see these URLs:
# http://www.cookbook-r.com/Graphs/Colors_(ggplot2)/
# https://r-graph-gallery.com/42-colors-names.html
useColor <- c("Treat all" = "black", "Treat none" = "grey",
              "Logistic regression" = "red", "CART" = "blue",
              "CARTcp02" = "cyan3", "CARTcp03" = "deepskyblue2",
              "CARTcp04" = "darkorchid", "CARTcp05" = "aquamarine3")

# Custom function to generate the harm-to-benefit second x-axis
htbPlot <- function(x) paste0("1:", round((1-x)/x, digits=1))

# Plot the decision curves
ggplot(data=dcaDf, aes(x=threshold, y=net_benefit, colour=label)) +
    geom_line(aes(colour=label, linetype=label, linewidth=label)) +
    
    labs(color=NULL) +
    coord_cartesian(ylim=c(-.0025, .015)) +
    
    # # Without 0% and 1:Inf
    # scale_x_continuous(
    #     breaks = seq(0.005, 0.02, by=.0025),
    #     labels = c("0.5%", "0.75%", "1%", "1.25%", "1.5%", "1.75%", "2%"),
    #     sec.axis = dup_axis(name="Harm-to-benefit ratio", labels=htbPlot)) +
    
    # With 0% and 1:Inf
    scale_x_continuous(
        breaks = seq(0, 0.02, by=.0025)[-2],
        labels = c("0%", "0.5%", "0.75%", "1%", "1.25%", "1.5%", "1.75%", "2%"),
        sec.axis = dup_axis(name="Harm-to-benefit ratio", labels=htbPlot)) +
    
    scale_colour_manual(values = useColor) +
    
    scale_linetype_manual(values = c("solid", "solid", "solid", "solid", "dashed",
                                     "dashed", "dashed", "solid")) +
    
    scale_linewidth_manual(values = c(1, 1, 1, 1, 0.3, 0.3, 0.3, 1)) +

    guides(linetype="none") +
    
    guides(linewidth="none") +
    
    ylab(label="Net benefit") +
    theme(
        panel.background = element_blank(),
        axis.text.x=element_text(size=16),
        axis.title.x=element_text(size=16),
        axis.text.y=element_text(size=16),
        axis.title.y = element_text(size=16),
        panel.border = element_rect(color="black", fill=NA),
        legend.text = element_text(size=14),
        legend.position = "top",
        legend.title = element_blank()) +
    labs(x="Threshold probability")
```

**Note.** The plot itself is shown in the publication and/or the other supplementary material. You can generate the plot yourself by using the R script 'G_CARTsensitivityAnalysis', which is part of this supplementary R package (see folder 'rscriptsVignettes').

**References**

Wickham H (2016). *ggplot2: Elegant Graphics for Data Analysis*. Springer-Verlag New York. ISBN 978-3-319-24277-4, [https://ggplot2.tidyverse.org](https://ggplot2.tidyverse.org).